The role of advection versus diffusion in intraventricular transport

### 2025-03-06 paper/main.tex
Updates in Comp methods  1

\subsection{Image-based computational geometries of zebrafish brain ventricles}
To model flow and transport in zebrafish larval brain ventricles, we generated a
3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
The standard mesh consisted of 132 134 tetrahedral cells and had a
maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
which are connected by interventricular ducts. 
Parts of the ventricular surfaces were marked to be lined with
motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.

The morphology and geometry of the brain ventricles vary across zebrafish
individuals, and under physiological and pathological conditions~\cite{Olstad2019CiliaryDevelopment}. 
Motivated by an interest in how ventricular geometry impacts solute distribution,
we also consider four variations in the geometry (cross-sectional area
reduction in parentheses):
by shrinking the fore-mid brain connection (66 \%), 
the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.
We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
% Cross-sectional areas of ducts normal to flow direction
% Modified region       Original mesh        Deformed mesh
% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
% Hind                  2.91e-3 mm^2         1.67e-3 mm^2

>>>>

\subsection{Image-based computational geometries of zebrafish brain ventricles}
To model CSF flow and transport in the zebrafish brain ventricles, we
generated a 3D surface representation of the ventricular walls using
confocal imaging data of a zebrafish embryo injected
intraventricularly with a 70 kDa dye at 2
dpf~\cite{Olstad2019CiliaryDevelopment}. At 2 dpf, the ventricular
system consists mainly of 3 cavities: the telencephalic (anterior),
the di-/mesencephalic (middle) and the rhombencephalic (posterior)
ventricles, which are connected by interventricular ducts. From the
surface geometry, we constructed a volumetric mesh of the ventricles
using fTetWild~\cite{Hu2020FastWild}, consisting of 132 134
tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu
m (4.68 \textmu m) (\Crefpanels{fig:fig1}{d}). Parts of the
ventricular surfaces were marked to be lined with motile cilia
(\Crefpanels{fig:fig1}{d}, magenta
markers)~\cite{Olstad2019CiliaryDevelopment}.

The morphology and geometry of the brain ventricles vary across zebrafish
individuals, and under physiological and pathological conditions~\cite{Olstad2019CiliaryDevelopment}. 
Motivated by an interest in how ventricular geometry impacts solute distribution,
we also consider four variations in the geometry (cross-sectional area
reduction in parentheses):
by shrinking the fore-mid brain connection (66 \%), 
the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.
We used Blender~\cite{Community2018BlenderPackage} to modify the geometries (\Crefpanels{fig:fig6}{a, b}).
% Cross-sectional areas of ducts normal to flow direction
% Modified region       Original mesh        Deformed mesh
% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
